Selective enhancement of an exploited species undermines community stability

### 2021-11-30 rmd/manuscript.Rmd
edit: manuscript

---
title: "Selective enhancement of an exploited species undermines the community stability"
output:
  word_document:
    reference_docx: word_format.docx
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
---

@@

Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to sustainable management of natural resources. Captive breeding is a pervasive method to conserve or enhance wild populations of diverse plant and animal taxa. In fisheries for example, XXX have been spent annually to support hatchery programs globally. There is growing recognition that the selective enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles); nevertheless, captive breeding is still widespread in conservation and fisheries perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks. However, a crucial yet overlooked perspective in this research area is the community-wide impact of selective enhancement through species interaction networks. Species are all embedded in the web of interacting organisms, and excessive release of particular species may have cascading consequences for ecological communities in the long term. Evidence for this hypothesis is lacking, however.

Here, we use a simple, general theory to show that the selective enhancement of a particular species undermines the community stability, which is defined here by the relative size of fluctuations in summed community density over time. The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with Japanese stream fish communities, in which an exploited species, masu salmon (*Oncorhynchus masou masou*), is supplemented through captive breeding programs.

We developed...

## Methods

>>>>

---
title: "Selective enhancement of an exploited species undermines community stability"
output:
  word_document:
    reference_docx: word_format.docx
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
---

@@

Anthropogenic influences have caused global biodiversity crisis, such that human interventions are critical to sustainable management of natural resources. Captive breeding - DEFINE CAPTIVE BREEDING - is a common method to conserve or enhance wild populations of diverse plant and animal taxa. Although there is growing recognition that the selective enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles), this method is still pervasive in conservation and fisheries. In fisheries for example, XXX have been spent annually to support hatchery programs globally. This is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks. The current debate, however, overlooks the fact that we have rarely assessed the community-wide impact of selective enhancement. Species are all embedded in the complex web of interacting organisms, and excessive release of particular species may have unforeseen consequences for ecological communities in the long term. Evidence for this hypothesis is lacking, however.

Here, we use a simple, general theory to show that the selective enhancement of a particular species undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time. The present study further demonstrates the relevance of this general theory to natural systems by illustrating its congruence with stream fish communities, in which an exploited species, masu salmon (*Oncorhynchus masou masou*), is supplemented by hatchery programs. Our findings paint a bleak picture for this form of ecosystem management, reinforcing the recurrent calls for alternative strategies.

We use a multispecies Ricker model to simulate community dynamics with selective enhancement of a particular species. Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species (species 1; set constant as $R_t = R$ for simplicity), and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations. The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species. XX parameter combinations were used to represent ecological scenarios with different strength of competition and XX. Under each simulation scenario, we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with varying $R$, of which the last 1000 time steps were used to obtain the coefficient of variation, mean, and standard deviation of community density ($\sum_i^SN_j$). Temporal means and standard deviations were calculated for the enhanced species $N_1$ and the unenhanced species $\sum_{i,i \ne 1}^S N_i$ separately to infer mechanisms that underlie community-level responses.

Our model predicted a destabilizing effect of selective enhancement on ecological communities. With increasing released individuals $R$, communities showed greater temporal fluctuations as illustrated by increased CV (Figure XX). Since CV is a ratio of SD to mean, the increase of CV can be driven by a decreased mean, an increased SD, or both. In our case, the group-level analysis depicted a major influence of the decreased means of enhanced and unenhanced species groups (Figure XX). For enhanced species, intraspecific competition is responsible for the decreased mean. That is, released individuals induce strong overcompensation, where the negative effect of reduced per-capita reproduction exceeds the numerical benefit (increased reproducing individuals) of released individuals. Meanwhile, the decreased mean of unenhanced species is caused by interspecific competition between enhanced and unenhanced species. This negative effect of released individuals through competition was noticeable even with weak interspecific competition that would otherwise allow stable coexistence. Combined, the total community density decreased more sharply than individual species groups with increased numbers of released individuals (XX). The SDs showed a similar trend, but the relationship was flatter than the means. CONCLUDING SENTENCE

ADDITIONAL PARAGRAPH ABOUT EXTERNAL CONTROL OF RELEASED INDIVIDUALS

EMPIRICAL ANALYSIS

### Methods
